Data Preparation

### 2019-01-10 Data Preparation.Rmd
debug import section

```{r setup, message = FALSE}
library(tidyverse)
library(tidytext)

library(gsheet) # import spreadsheets from google drive
library(tm)
library(hunspell) # Stemmer

library(rlist)
#library(tidyr) #(maybe incuded in tidyverse)
#library(tibble)
```

@@

lists <- list(
  Assessment      = lists_brut$Assessment,
  Assessment_plot = lists_brut$Assessment[lists_brut$`Assessment for Plot` == 1],
  AoD             = lists_brut$Aim[!is.na(lists_brut$Aim)],
  AoD_plot        = lists_brut$Aim[lists_brut$`Aim for Plot`[!is.na(lists_brut$Aim)] == 1]
  )
```

@@

### Course Catalogues
In order to conduct a preliminary topic modeling of course content, we first analyze their description in the course catalogues. The corpus `corpus` contains the pdfs of the `5` most recent course catalogues.
```{r corpus, cache = TRUE}
corpus <- Corpus(x             = DirSource("Catalogues"),
                 readerControl = list(reader = readPDF(control = list(text = "-layout"))))
```

### Course Manuals
To expand our topic modeling of course content, we would like to analyse the material in the course manuals. The `corpus_manuals` contains the pdfs of the course manuals for the year 2017-2018 (most recently, available).
```{r}
corpus_manuals <- Corpus(x             = DirSource("Manuals 2017-18"),
                 readerControl = list(reader = readPDF(control = list(text = "-layout"))))
```
## Student Data
The tibble `transcripts` contains the transcripts of a selection of `7` alumni students from the college[^2]. `transcripts` contains information on each course taken by each student such as the receives grade, the semester in which teh course was taken as well as the calendar year.
```{r transcripts}
transcripts <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1kj7tlfJAoN0F7IdoS3saT-2iC3nuDLwnDItNtCKoZ4k/edit#gid=936718979')
print(transcripts)
```
COMMENT SOFIA: save a_clean_transcript as d_transcript

@@

```{r Data Import}
t1 <- read.csv("Raw Grades/grades1.csv",na.strings=c("","NA"))
t2 <- read.csv("Raw Grades/grades2.csv",na.strings=c("","NA"))
d_dirt <-rbind(t1, t2)
d_dirt <- d_dirt[!duplicated(d_dirt),] #could use distinct() from dplyr
```

@@

```{r overview}
# Setup
n_catalogue <- length(corpus)
calendar_years <- c("2014-2015", "2015-2016", "2016-2017", "2017-2018", "2018-2019")
d_description <- tibble(Code            = character(0),
                        `Calendar Year` = character(0),
                        Overview        = character(0))

@@

  cat <- content(corpus[[n]])

>>>>

```{r libraries, message = FALSE}
library(tidyverse)
library(tidytext)

library(gsheet) # import spreadsheets from google drive
library(tm)
library(hunspell) # Stemmer
#library(rlist)
```

@@

lists <- list(
  Assessment      = lists_brut$Assessment,
  Assessment_plot = lists_brut$Assessment[lists_brut$`Assessment for Plot` == 1],
  AoD             = lists_brut$Aim[!is.na(lists_brut$Aim)],
  AoD_plot        = lists_brut$Aim[lists_brut$`Aim for Plot`[!is.na(lists_brut$Aim)] == 1]
  )

rm(lists_brut)
```

@@

### Course Catalogues
In order to conduct a preliminary topic modeling of course content, we first analyze their description in the course catalogues. The corpus `corpus_catalogues` contains the pdfs of the `5` most recent course catalogues.
```{r corpus_catalogues, cache = TRUE}
corpus_catalogues <- Corpus(x             = DirSource("Catalogues"),
                            readerControl = list(reader = readPDF(control = list(text = "-layout"))))
```

### Course Manuals
To expand our topic modeling of course content, we would like to analyse the material in the course manuals. The `corpus_manuals` contains the pdfs of the course manuals for the year 2017-2018 (most recently, available).
```{r corpus_manuals, cache = TRUE}
corpus_manuals <- Corpus(x             = DirSource("Manuals 2017-18"),
                         readerControl = list(reader = readPDF(control = list(text = "-layout"))))
```

## Student Data
The tibble `transcripts` contains the transcripts of a selection of `7` alumni students from the college[^2]. `transcripts` contains information on each course taken by each student such as the receives grade, the semester in which teh course was taken as well as the calendar year.

COMMENT SOFIA: save a_clean_transcript as d_transcript

@@

```{r Data Import}
d_transcript <- rbind(read_csv("Raw Grades/grades1.csv", na.strings=c("","NA")),
                      read_csv("Raw Grades/grades2.csv",na.strings=c("","NA"))) 
d_transcript <- d_transcript[!duplicated(d_transcript),] #could use distinct() from dplyr
```

@@

```{r overview}
# Setup
n_catalogue <- length(corpus_catalogues)
calendar_years <- c("2014-2015", "2015-2016", "2016-2017", "2017-2018", "2018-2019")
d_description <- tibble(Code            = character(0),
                        `Calendar Year` = character(0),
                        Overview        = character(0))

@@

  cat <- content(corpus_catalogues[[n]])
